% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.


%To Do:
%   - GPA is @ 2.949... Round to 2.95, which rounds to 3.00
%  http://www.tvmier.com/Resume_Education.html
%   - Continuously update skills learned from TS
%   - Continuously Update projects learned from TS


\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[utf8]{inputenc} %kodovani
\usepackage[czech, english]{babel}
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\project}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}
\newcommand{\myheader}{
\begin{center}
\textbf{\Huge Ing. DAVID VÁVRA}
\end{center} 
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	Prague, Czech Republic &  \href{mailto:david@vavra.me}{david@vavra.me} \\
	\end{tabular*}
\\
\vspace{0.1in}}

\myheader


%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
	\item 
			\ressubheading{\href{https://airbank.net}{Air Bank Germany}}{Prague}{Lead Android Developer}{from Nov. 2016}
				{ \footnotesize
				\begin{itemize}
					\resitem{Leading Android team of 5 developers }
					\resitem{Refactoring Android architecture of the app to use Kotlin/DI/Navigation/MVVM }
					\resitem{Replacing part of backend data from GraphQL to Firestore}
					\resitem{Coordinating QA, CI/CD pipelines and automated testing}
					
				\end{itemize}
				}	
	\item 
			\ressubheading{\href{https://stepuplabs.io}{Step Up Labs Inc.}}{Prague}{CEO \& Dev Lead}{from Mar. 2016}
				{ \footnotesize
				\begin{itemize}
					\resitem{Founded a US company for my app Settle Up}
					\resitem{Coordinating a team of 5, leading development, building the Android app}
					\resitem{Settle Up has over 250K monthly active users, it's available on Android, iOS, Windows \& web}
					\resitem{It's used globally: 27\% Spain, 27\% India, 5\% Italy, 5\% Germany, 5\% Czechia}
					\resitem{4.4 rating, monetization with ads \& subscriptions on Android, paid app on iOS}
					
				\end{itemize}
				}	
	    \item 
			\ressubheading{\href{http://www.avast.com}{Avast Software s.r.o}}{Prague}{Android Developer and Developer Advocate}{Aug. 2014 -- Feb. 2016}
				{ \footnotesize
				\begin{itemize}
					\resitem{Wrote production code for Avast Android apps and libraries}
					\resitem{Worked on Avast Mobile Security (100M+ installs) and Avast Anti-Theft (10M+ installs)}
					\resitem {Coordinated the company’s open-source efforts, managed developer-focused social media, organized dev
events, spoke at international conferences}
				\end{itemize}
				}	
	    \item 
			\ressubheading{\href{http://www.inmite.eu}{Inmite s.r.o.}}{Prague}{Android Developer and Developer Advocate}{Oct. 2012 -- Jul. 2014}
				{ \footnotesize
				\begin{itemize}
					\resitem{Responsible for a the full development cycle of Android apps}
					\resitem {Started developer relations for the company, started initiative \href{http://inmite.github.io/}{"Inmite Developers"}, publicly speaking about our open-source libraries.}
					\resitem{Working on apps for clients like \href{https://play.google.com/store/apps/details?id=cz.o2.moje}{Telefonica O2}, \href{https://play.google.com/store/apps/details?id=eu.inmite.prj.skoda.service}{Škoda Auto} or \href{https://play.google.com/store/apps/details?id=com.czechtourism.top100.android}{CzechTourism}}
				\end{itemize}
				}
	    \item 
			\ressubheading{\href{http://www.google.com}{Google UK Ltd.}}{London, UK}{Mobile Developer Intern}{Jul. 2011 -- Dec. 2011}
				{ \footnotesize
				\begin{itemize}
					\resitem{Built system \href{http://code.google.com/p/quiz-and-poll/}{Quiz \& Poll}, used for internal trainings (instead of costly hardware clickers), open-sourced}
					\resitem{Implemented whole stack - Android app, Web player, AppEngine backend, Google Apps Script interface}
					\resitem{Participated in external Android project in 20\% time}
				\end{itemize}
				}
	    \item 
			\ressubheading{\href{http://www.bondaii.com}{Bondaii Ltd.}}{Prague}{Android Developer}{Sep. 2010 -- Jun. 2011}
				{ \footnotesize
				\begin{itemize}
					\resitem{Created Android client for start-up Bondaii, supervised iPhone developer}
				\end{itemize}
				}
	    \item 
			\ressubheading{\href{http://www.k-state.edu}{Kansas State University}}{Manhattan, KS, USA}{Web Developer}{Feb. 2010 -- May 2010}
				{ \footnotesize
				\begin{itemize}
					\resitem{Created webpages for research projects of Bio \& Ag Engineering Department}
				\end{itemize}
				}
	    
		\item 
			\ressubheading{\href{http://www.locify.com}{Locify Ltd.}}{Prague}{Co-founder and Mobile Developer}{Sep. 2007 -- Sep. 2009}
				{ \footnotesize
				\begin{itemize}
					\resitem{Helped to define the startup, Implemented mobile application in Java ME, supervised other developer}
				\end{itemize}
				}
		\item
			\ressubheading{\href{http://www.phonesoft.cz}{Phonesoft a.s.}}{Prague}{Junior Mobile Developer}{Sep. 2004 -- Sep. 2007}
				{ \footnotesize
				\begin{itemize}
					\resitem{Implemented several mobile applications in Java ME}
				\end{itemize}
          			}

	\end{itemize}  % End Experience list
	
	\newpage
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
                                                                                                                                                                                       %Current GPA: 2.88; GPA @ Midterm: 3.00; GPA after A in Internship 3.09!
			\ressubheading{\href{http://www.cvut.cz/en?set_language=en}{Czech Technical University}}{Prague}{Master's degree in Software Engineering and Interaction}{Sep. 2009 -- Jun. 2012}
				{ \footnotesize
				\begin{itemize}
					\resitem{\href{http://www.settleup.info/files/master-thesis-david-vavra.pdf}{Thesis: Settle Up - mobile app for group expenses, UX testing and monetization}}
					\resitem{Graduated with honors, GPA 3.536}
				\end{itemize}
				}
		\item
                                                                                                                                                                                       %Current GPA: 2.88; GPA @ Midterm: 3.00; GPA after A in Internship 3.09!
			\ressubheading{\href{http://www.k-state.edu}{Kansas State University}}{Manhattan, KS, USA}{Study abroad, major: Computer Science}{Sep. 2009 -- May 2010}
{ \footnotesize
				\begin{itemize}
					\resitem{GPA 3.679}
				\end{itemize}
				}
		\item   															%
			\ressubheading{\href{http://www.cvut.cz/en?set_language=en}{Czech Technical University}}{Prague}{Bachelor's Degree in Software Engineering}{Sep. 2006 -- Jun. 2009}
				{ \footnotesize
				\begin{itemize}
					\resitem{\href{http://www.destil.cz/bachelor-thesis-david-vavra.pdf}{Thesis: Catch\&Run - mobile multiplayer GPS game}}
					\resitem{Graduated with honors, GPA 3.695}
				\end{itemize}
				}
	\end{itemize} % End Education list	
	
	
%%%%%%%%%%%%%%%%%
\resheading{Accomplishments}
\begin{itemize}
	\item
	\href{https://developers.google.com/experts/}{Google Developer Expert for Android} (since 2015), spoke at 15 conferences outside Czechia
	\item{Coorganized \href{http://www.devfest.cz/}{DevFest CZ conference} (2012, 2013, 2014, 2017 as main organizer)}
	\item{Coorganized \href{http://www.devfest.cz/}{mDevCamp conference} (2013, 2014, 2015, 2016, 2018, 2019 as core organizer)}
	\item
	\href{https://www.youtube.com/watch?v=6z3ScqblqFk}{Guest in a popular 'Show Jana Krause' in public TV with Google Glass} (2014)
	\item Organized 16 meetups for Android developers in 2014 and 3 meetups for Kotlin developers in 2018
	\item \href{http://www.diplomovaprace.cz/}{Winner of 'Czech Master's Thesis of the Year' contest} (2012)
	\item  \href{http://www.google.com/intl/en/jobs/students/proscho/programs/emea/ambassador/}{Google Student Ambassador} at Czech Technical University (2011/2012)
	\item 'Wild card' from Vodafone CZ at \href{http://www.mediar.cz/treti-prehlidku-appparade-ovladly-aplikace-pro-android-zvitezil-night-walker-tomase-zveriny/}{AppParade} contest with Android app \href{https://market.android.com/details?id=cz.destil.settleup}{Settle Up} (2011)
	\item Winner of \href{http://hackathonbrno.blogspot.com/2010/06/v-nabite-aule-jsme-odprezentovali-9.html}{first hackathon in Czechia} (2010)
	\item $2^{nd}$ place in local ACM Programming Contest at K-State (2010) 
	\item CTU scholarship for excellent results (2006-2009)
	\item \href{http://www.juniorinternet.cz/winners/307/david-vavra.aspx}{Winner of JuniorInternet 2003 with my project 'Duna on-line'}
\end{itemize}	
	
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}

\begin{itemize}
	 \item Software:
		 \begin{itemize}
	 		\footnotesize
			\resitem{Android architecture, Kotlin, reactive \& functional programming, Unit \& UI testing, dependency injection}
			\resitem{Firebase, Google Cloud Platform, Angular}
		 \end{itemize} 	
	\item Languages:
		\begin{itemize}
			\footnotesize
			\resitem{Czech (native speaker)}
			\resitem{English (fluent in speaking, excellent in listening, reading and writing, TOEFL score: 108/120)}
			\begin{itemize}
			\resitem{Attended US university for one year (2009/2010)}
			\resitem{English courses in Sydney, Australia (2004), Malta (2003) and Hastings, UK (2002)}
			\end{itemize}
			\resitem{German (basic reading and writing skills) }
		\end{itemize}	
	\item Personal:
		\begin{itemize}
			\footnotesize
			\resitem{Public speaking, Organizing developer events,, Leadership skills,  Reliable, MBTI personality: INTJ}
		\end{itemize}			
\end{itemize}

%%%%%%%%%%%%%%%%%
\resheading{Interests and activities}
\begin{itemize}
	\item Playing live action role playing games (LARPs) and board games
	\item Interest in travelling, geocaching, swimming, snowboarding, \& gardening
\end{itemize}
\end{document}
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l }
			
			Anita Flanagan & Kerri Ebert \\
			Google Inc. & Kansas State University \\
			Learning Technology PM & Research and Extension Coordinator \\ 
			\vspace{10pt} 
			Dublin, IR & Manhattan, KS, USA \\ 
			\href{mailto:aflanagan@google.com}{aflanagan@google.com} & \href{mailto:kebert@k-state.edu}{kebert@k-state.edu} \\
		\end{tabular*}
	\end{center}







%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".  Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.
	
	\begin{description}
		\item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
		\item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
		\item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
		\item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.} 
		\item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.	ADC0809), and PCB design}
		\item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
		\item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
		\item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
		\item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
		\item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
	\end{description}


\resheading{Software Engineering Projects}  % There really are a TON of project I can put on this, but here are some major ones:
	\begin{description}
		\item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
		\item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
		\item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
		\item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
		\item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
		\item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
	\end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Toby Rummans & Eric Karl & Gordon Smith \\
			Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
			\vspace{10pt} 
			Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
			3700 E Jewell Ave \# 225 & 525 South Center St. & 525 South Center St.  \\
			Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
			(303) 349-3469 & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}
	
% \end{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARCHIVED INFORMATION FOR ADDITIONAL RESOURCES      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ADDITIONAL REFERENCE BLOCK (TEACHER, TEACHER, EMPLOYER)
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Kevin Twitchell & Eric Karl & Gordon Smith \\
			Computer Science \& Engineering & Computer Science \& Engineering  & Technology Support Specialist \\
			\vspace{10pt}    
			BYU-Idaho & BYU-Idaho & BYU-Idaho \\
			525 South Center St. & 525 South Center St. & 525 South Center St.  \\
			Rexburg ID 83460 & Rexburg ID 83460 & Rexburg ID 83460 \\
			(208) 496-1938 & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

		\item 
			\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
				{ \footnotesize
				\begin{itemize}
	            			\resitem{Managed file and application servers running Windows 2003 Server}
	            			\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
				\end{itemize}
				}

		\item 
			\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
				{ \footnotesize
				\begin{itemize}
					\resitem{Provided Bresnan customers with technical support over the phone.}
					\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
				\end{itemize}
				}

		\item 
			\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
				\begin{itemize}
					\resitem{Interned with full time Gas/Electrical Engineers.}
					\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
				\end{itemize} 


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/
